---
title: "WebTS Report"
date: "26 12 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

case_sep <- function(expr1, expr2){ #quick way to determine the case we are dealing with, i.e. consumption or unemployment
  switch(input$target, "Unemloyment" = expr1, "Consumption" = expr2)
}
```

#Target Series
The target series is chosen to be the `r paste0(input$target, case_sep("rate",""))` of `r paste(names(input$region))`. The data was retrieved from Eurostat as the following:

```{r plot eurostat}

    target_ts <- eurostat_query() #load the eurostat data from the output of eurostat_query
    autoplot.zoo(target_ts) #

```

#Hitwords
To predict the target series, the followng words were used:

```{r keywords}

  user_words <- strsplit(input$keyword, ",")[[1]]  #get keywords to use from user input and save it to variable keyword
  
  Keyword <- colnames(google_query())
  Source <- rep("Auto",length(Keyword))
  Source[which(Keyword %in% user_words)] <- "User"
  
  pander(rbind(seq_len(length(Keyword)),Keyword,Source))

```

Where less than five words are specified, the rest is added automatically using the most related hitwords from Google trends. The Trend series look like the following:


```{r plot google}

    query_ts <- google_query() #load the google trend series from the output of google_query
    autoplot.zoo(query_ts) #autolpot the series using ggplot2

```


#The Model

`r if(input$end_difflog==T) print("Before any further computation is done, the natural logarithm of the target series is taken, and the outcome is differentiated one times, to retrieve growth rates.");if(input$exo_difflog==T) print("The same is applied to the explaining Google Trend data")`
On these data, a PCA is performed and the resulting components are are lagged for `r paste(input$nahead[[1]])` to `r paste(input$nahead[[2]])` periods.
Furthermore, an iterating selection process is run, specifying an OLS according to the AIC. The final model is sepcified to be:

```{r model}
    
    model <- analysis()[[1]]
    print(summary(model))

```

and yileds the following forecast:

```{r plot fitted}
    
    Predicted <- analysis()[[2]] #read in fitted values from analysis reacrive
    Historical <- eurostat_query() #original series from eurostat API
    
    #Prepare data for ggplot
    plot_fitted <- fortify.zoo(cbind(Predicted,Historical))
    plot_fitted <- melt(plot_fitted, id = "Index")
    
    #ggplot
    ggplot(plot_fitted, aes(x = Index, y= value, color = variable )) + geom_line() +
      theme(legend.position = "bottom", legend.title = element_blank())  + xlab("Time") +
      ylab("Value")

```


The following test were run:
```{r tests}
    
# run tests
test_results <- test_dir(getwd(), reporter="summary")

# test results
print(test_results)

```




